An Open Platform for Managing Short Programming Exercises

### 2013-06-24 paper/paper.tex
clarification about spring 2013 CS101 at YCP

In the Spring 2013 term at York College, we used CloudCoder in a CS1
class, taught in C, with 122 students.  There were more than 56,000
submissions for 68 exercises.  Because using CloudCoder was the
only change in pedagogy compared to previous offerings of the course,
we plan to analyze this data to see if we can find evidence that
the exercises resulted in improved outcomes.

>>>>

In the Spring 2013 term at York College, we used CloudCoder in a CS1
class, taught in C, with 122 students.  There were more than 56,000
submissions for 68 exercises.  Because using CloudCoder was the
only major change in pedagogy compared to previous offerings of the course,
we plan to analyze this data to see if we can find evidence that
the exercises resulted in improved outcomes.
